\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-15 manuscript.Rmd
Updated Flowchart1

                    graph [fontname = Helvetica,layout = dot,fontsize = 20, ]

                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
                    fixedsize = true,fontsize = 20]

@@

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 7.5, height = 2, 
                    fixedsize = true, fontsize = 20]
                    C[label = 
                    <
                    Factor Identification<br align = 'left'/>
                    Scree Plot: 6 Factors<br align = 'left'/>
                    Parallel Analysis: 6 Factors<br align = 'left'/>
                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
                    Hull Method: 5 Factors<br align = 'left'/>
                    >
                    ]

                     subgraph cluster_1 {
                      graph[fontname = Helvetica, shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 9, height = 1, 
                    fixedsize = true, fontsize = 18 ]

                     1[label = '5 Factor Solution Retained 25 Items']
                     2[label = 'Reliability Analysis on EFA Sample (N=428)
                    Alpha F1 =.86; F2 = .71; F3 = .68; F4 =.62; F5 =.52']

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
                    8[label = 'LEBA Short Form (17 Items; N=690) 
                      Based on Item Response Theory']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 8, height = 1, 
                fixedsize = true, fontsize = 18 ]
                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
                    7[label = 'Rejected']
                    }

                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     4 ->5
                    5->8
                     C ->6
                     6 ->7

}")

export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/Flowchart1.png")

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='150%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.png')
```

@@

{rank = same; F1 F2 F3 F4 F5}
# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 35]
F5 -> u [label = '0.60']
F5 -> v [label = '0.59']
F5 -> w [label = '0.41']
F5 -> x [label = '0.41']
F5 -> y [label = '0.40']
F5 -> z [label = '0.35']
F4 -> p [label = '0.74']
F4 -> q [label = '0.73']
F4 -> r [label = '0.66']
F4 -> s [label = '-0.39', color =red]
F4 -> t [label = '0.39']
F3 -> k [label = '0.80']
F3 -> l [label = '0.80']
F3 -> m [label = '0.65']
F3 -> n [label = '0.49']
F3 -> o [label = '36']
F2 -> e [label = '0.79']
F2 -> f[label = '0.76']
F2 -> g [label = '0.65']
F2 -> h[ label = '0.50']
F2 -> i [label = '-.49',color =red]
F2 -> j [label = '0.32']
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
}
")

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/EFAplot.png")

@@

Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by  RMSEA value obtained from Signed-$\chi^2$ index implementation. All of the items had RMSEA value <.06 indicating adequate fit. Figure \@ref(fig:personfit) depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018]. We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh < -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
```{r itemfittab, results='asis',warning=F, message=F}
apa_table(itemfit, caption ="Item fit statistics for the fitted models")
```

>>>>

                    graph [fontname = Helvetica,layout = dot,fontsize = 40, ]

                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 15, height = 1, 
                    fixedsize = true,fontsize = 40]

@@

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 15, height = 6, 
                    fixedsize = true, fontsize = 40]
                    C[label = 
                    <
                    Factor Identification<br align = 'left'/>
                    Scree Plot: 6 Factors<br align = 'left'/>
                    Parallel Analysis: 6 Factors<br align = 'left'/>
                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
                    Hull Method: 5 Factors<br align = 'left'/>
                    >
                    ]

                     subgraph cluster_1 {
                      graph[fontname = Helvetica, shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
                    fixedsize = true, fontsize = 38 ]

                     1[label = '5 Factor Solution Retained 25 Items']
                     2[label = 'Reliability Analysis on EFA Sample (N=428)
                    Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62']

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52']
                    8[label = 'Measurement Invariance Analysis
                    Residual measurement invariance achieved']
                    9[label = 'Semantic Analysis']
                    10[label = 'LEBA Short Form (17 Items; N=690) 
                      Based on Item Response Theory']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
                fixedsize = true, fontsize = 38 ]
                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
                    7[label = 'Rejected']
                    }

                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     4 ->5
                    5->8
                    8 ->9
                    9 ->10
                     C ->6
                     6 ->7

}")
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/Flowchart1.png", dpi = 1200)

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.png')
```

@@

# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 35]
F5 -> u [label = '0.60']
F5 -> v [label = '0.59']
F5 -> w [label = '0.41']
F5 -> x [label = '0.41']
F5 -> y [label = '0.40']
F5 -> z [label = '0.35']
F4 -> p [label = '0.74']
F4 -> q [label = '0.73']
F4 -> r [label = '0.66']
F4 -> s [label = '-0.39', color =red]
F4 -> t [label = '0.39']
F3 -> k [label = '0.80']
F3 -> l [label = '0.80']
F3 -> m [label = '0.65']
F3 -> n [label = '0.49']
F3 -> o [label = '36']
F2 -> e [label = '0.79']
F2 -> f[label = '0.76']
F2 -> g [label = '0.65']
F2 -> h[ label = '0.50']
F2 -> i [label = '-.49',color =red]
F2 -> j [label = '0.32']
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
}
")

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/EFAplot.png", dpi = 1200)

@@

Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by  RMSEA value obtained from Signed-$\chi^2$ index implementation. All of the items had RMSEA value $\le$.06 indicating adequate fit. Figure \@ref(fig:personfit) depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018]. We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh < -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
```{r itemfittab, results='asis',warning=F, message=F}
apa_table(itemfit, caption ="Item fit statistics for the fitted models")
```
